Sumbission Steps

### 2021-01-07 code/03-submission-steps.Rmd
prepared all files for submission
final prep for resubmission

    ```{r}
    # Specify date of submission folder
    submission_date = "2021-01-06"

@@

    # Folders to delete
    unlink("../figure", recursive = TRUE)
    unlink(submission_folder, recursive = TRUE)
    unlink("../support-info/figure", recursive = TRUE)
    ```

@@

10. Knit this document to make sure the md version is up to date.

>>>>

    ```{r}
    # Specify date of submission folder
    submission_date = "2021-01-07"

@@

    # Folders to delete
    unlink("../figure", recursive = TRUE)
    unlink("../support-info/figure", recursive = TRUE)
    unlink(submission_folder, recursive = TRUE) 
    ```

@@

11. Use latexdiff to generate a pdf showing the differences between the this submission and the previous one. To do this, (i) run the R code below, (ii) run the code `latexdiff submissions/2020-10-07/paper.tex submissions/2021-01-07/paper.tex > submissions/2021-01-07/diff/2020-10-07-to-2021-01-07.tex` in the terminal (changes dates in the code as needed), and (iii) knit the generated tex file to make sure the pdf with the changes looks good.

    ```{r}
    # Create folder to place the diff
    diff_folder = paste0("../submissions/", submission_date, "/diff")
    dir.create(diff_folder)

    # Create folders within diff to store the figures needed
    dir.create(paste0(diff_folder, "/figure"))
    dir.create(paste0(diff_folder, "/figure-static"))

    # Copy necessary files into the diff folder needed for the diff to work
    file.copy("../references.bib", diff_folder)
    file.copy("../WileyNJD-AMS.bst", diff_folder)
    file.copy("../WileyNJD-v2.cls", diff_folder)
    file.copy(list_of_generated_figures, paste0(diff_folder, "/figure"))
    file.copy(list_of_static_figures, paste0(diff_folder, "/figure-static"))
    ```

12. Knit this document to make sure the md version is up to date.
